Clouds and Sensitivities Across a Hierarchy of GFDL CMIP6 Models

### 2020-11-03 Silvers_cfmip_MISR_cloudtable.tex

\begin{figure}
  \centering
  \subfloat{
  \includegraphics[width=0.2\linewidth]{cfmipfigs/cloud_table_misr_am4_glbmn.eps}}
%\end{subfigure}
  \subfloat{
  \includegraphics[width=0.2\linewidth]{cfmipfigs/cloud_table_misr_am4_sh_30t60.eps}}
  \subfloat{
  \includegraphics[width=0.2\linewidth]{cfmipfigs/cloud_table_misr_am4_pm30.eps}}
\subfloat{
  \includegraphics[width=0.2\linewidth]{cfmipfigs/cloud_table_misr_am4_nh_30t60.eps}}
\end{figure}

>>>>

\begin{figure}
  \centering
  \subfloat{
  \includegraphics[width=0.2\linewidth]{/Users/silvers/code/silversCFMIP/cloud_table_misrV7_am4_glbmn.eps}}
%\end{subfigure}
  \subfloat{
  \includegraphics[width=0.2\linewidth]{/Users/silvers/code/silversCFMIP/cloud_table_misrV7_am4_sh_30t60.eps}}
  \subfloat{
  \includegraphics[width=0.2\linewidth]{/Users/silvers/code/silversCFMIP/cloud_table_misrV7_am4_pm30.eps}}
\subfloat{
  \includegraphics[width=0.2\linewidth]{/Users/silvers/code/silversCFMIP/cloud_table_misrV7_am4_nh_30t60.eps}}
\end{figure}

### 2020-11-03 Silvers_cfmip_SinglePanelFig.tex

\begin{figure}
  \centering
  \begin{subfigure}{0.48\textwidth}
  \includegraphics[width=\linewidth]{cfmipfigs/CRE_net_ceres_cfmipExps.eps}
\end{subfigure}
\begin{subfigure}{0.48\textwidth}
  \includegraphics[width=\linewidth]{cfmipfigs/CRE_SWonly_feedback_amip.eps}
\end{subfigure}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{subfigure}{0.31\textwidth}
    \includegraphics[width=\linewidth]{/Users/silvers/Research/cfmip_paper/cfmip_cf_climo-eps-converted-to.pdf}
\end{subfigure}
\begin{subfigure}{0.31\textwidth}
  \includegraphics[width=\linewidth]{/Users/silvers/Research/cfmip_paper/cfmip_cf_vs_piC-eps-converted-to.pdf}
\end{subfigure}
\begin{subfigure}{0.31\textwidth}
  \includegraphics[width=\linewidth]{/Users/silvers/Research/cfmip_paper/cfmip_cf_vs_amip-eps-converted-to.pdf}
\end{subfigure}
\end{figure}

### 2020-11-03 Silvers_cfmip_draft.tex

\documentclass[11pt]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{epstopdf}
%\usepackage{pdflatex}
%\usepackage{epsfig}

@@

\begin{abstract}
The newest atmospheric climate model at GFDL, AM4, succeeded at significantly reducing the TOA radiative flux biases as compared to CERES observations.  Despite a relatively low top-of-atmosphere sensitivity to uniform warming of SSTs (Cess warming experiments), the corresponding coupled climate model, CM4, has high transient and equilibrium climate sensitivities.

@@

%\section{Key Questions}

\textbf{Key Points}
\begin{itemize}
  \item{The AM4.0 TOA cloud radiative effect shows small biases compared with CERES-EBAF observations, both versions 
  2.8 and 4.1.}
  \item{Too few clouds are simulated by AM4.0 at high, middle, and low-levels, as compared to observations from CALIPSO.}
  \item{Various configurations of a single global climate model lead to climate sensitivities that range from 2.1K (Cess) to 
  about 5K (Winton's ECS).}
\end{itemize}

@@

@@

\begin{figure}
% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 1
  \includegraphics[width=0.75\columnwidth]{cfmipfigs/clt_isccp_calipso_am4_4pan.eps}
  \caption{Comparison of total cloud fraction from AM4 with two observational data sets: ISCCP (left) and CALIPSO (right).}
  \label{fig:clt_isccp_calipso}
\end{figure}

\begin{figure}
% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 1
  \includegraphics[width=0.95\columnwidth]{/Users/silvers/Research/cfmip_paper/cf_misr_cldfrac_allheights.eps}
  \caption{Observed and modeled clouds.  Clouds shown are divided into thick (optical depth between 3.6 and 23) 
  and thin (optical depth between 0.3 and 3.6) 
  clouds.  The observations (bottom) are from the MISR satellite (2000-2013) and the modeled clouds (top) were 
  derived with the MISR simulator.  Data from all vertical levels is used.}
  \label{fig:misr}
\end{figure}

\begin{figure}
% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 3
  \includegraphics[width=0.86\columnwidth]{/Users/silvers/Research/cfmip_paper/cf_misr_cldfrac_below3km.eps}
  \caption{As in previous figure except that here only clouds below 3km are shown.  Clouds shown are divided into thick 
  (optical depth between 3.6 and 23) and thin (optical depth between 0.3 and 3.6) 
  clouds.  The observations (bottom) are from the MISR satellite (2000-2013) and the modeled clouds (top) were derived 
  with the MISR simulator (amip experiment).}
  \label{fig:calipso_sim_vs_mod}
\end{figure}

@@

@@

The recent model development efforts at GFDL, and participation in CMIP6/CFMIP have provided a 
unique/valuable opportunity to analyze a group of models that are built on the same code base while 
spanning a wide range of model configurations.  The model types include (should we include any of the
efforts from the RCE or Walker Cell configurations?) an Aquaplanet, and AGCM, 
and a AOGCM.  When combined with a variety of boundary conditions this creates a hierarchy of
models which are all derived from or dependent on the same atmospheric code base (AM4.0).  It is a 
bit like a group of siblings sharing the same gene pool but at various stages of intelligence or education.      
Our hypothesis for this study is that the large range of climate sensitivities that are found within this 
group of models is in large part due to variations in the clouds (both their climatology and their feedbacks).
The clouds in these simulations are responding to a variety of different conditions including different
patterns of prescribed SST, the presence or absence of land/ice, and in the case of the aquaplanet
experiments, a lack of cloud-aerosol interactions which is present in the amip and coupled experiments.

The DECK experiments of CMIP6 can be used to provide a measure of the climate sensitivity based on 
three different fully coupled experiments.  The methods used to determine the sensitivity are distinct, and the resulting 
differences in the measures of sensitivity reveal important details of the physics that underly the response
of the climate system to a perturbation such as increasing concentrations of carbon dioxide.  The three 
experiments are the historical simulation (historical: 1850-2014),  the abrupt quadroupling of CO2 concentration 
 (abrupt-4xCO2: 150 years), and the experiment in which the concentration of CO2 is increased by 1\% 
 per year from the pre-industrial until the concentration is doubled (1pctCO2: 150 years, doubling at year 70).  
The historical simulation is our best attempt at using our coupled GCM to reproduce the historical 
record found in observations.  This has frequently been used to estimate the climate sensitivity using the 
energy budget method (Otto et al., 2013, Armour et al., Andrews et al., Winton et al., 2020).  The abrupt-4xCO2
experiment has been utilized by the IPCC to derive measures ECS among the CMIP5 and CMIP6 models
using a linear regression of the change in TOA radiative fluxes and surface air temperature over the first 
150 years of simulation (Gregory et al., 2004; Andrews et al., 2012).  In contrast to the abrupt change of 
CO2 concentration, the 1pctCO2 experiment allows the Earth system to adjust to slowly increasing concentrations.  
The sensitivity taken from this experiment is argued to be more relevant for an assessment of the 
near term impact of the climate change because it is calculated based on a doubling of CO2.

@@

Plotting the cloud fields as a function of latitude and height highlights some of the similarities and differences 
between the various experiments.  In general the clouds in the amip and historical simulations are similar to 
each other, as we would expect.  The differences between the clouds of these experiments are due to the 
different SST pattern that the two experiments have.  We can thus see how the clouds change as a result 
of SST biases over the observational period.  Two warming experiments have been plotted, amip p4K and 
the coupled abrupt 4xCO2 experiment.  The cloud fields in these experiments are similar to each other, with 
the differences again likely coming from the different SST patterns that result from a fully coupled system.  The 
cooling experiment is rather unique and tends to have cloud fraction changes in the opposite direction as 
the warming experiments.

% Beta feedback??  relavent?
Brient and Bony (2012) proposed what they call the $\beta$ feedback as a way to quantify whether or not ' models have 
changes in low-cloud cloud radiative effects which are proportional to the strength of the cloud radiative effects of their
low clouds.'  See $\it{Stevens etal, Cookie Overview}$ for details.   That paper asks the question of whether single 
model relationships between low-cloud amounts and the sensitivity of low clouds to warming can be 
masked by changes in multi-model ensembles.  This should be checked for the GFDL model in this paper.

The cloud radiative effect (CRE) is computed as the difference between the all-sky and clear-sky TOA fluxes.

\begin{table}
\begin{center}
\caption{Global mean radiative feedbacks.  The cloud radiative effect (CRE) is computed as
 the clear sky minus all sky flux. The values for the Abrupt 4xCO2 experiment
have been estimated from a linear fit of the years 51-300.  Compare to Ringer et al. 2014.
Values in parenthesis are most recent values.  Why are they different than the Amip p4K 
original values?}
    \begin{tabular}{*{7}{c}}
    \hline
    \hline
 Feedback & Aqua p4K & Amip m4K & Amip p4K &  Amip p8K & Amip Future & Abrupt 4xCO2    \\ \hline
    Net          &   -2.2 (-2.2) & ?? (-1.9)  &  -1.6 (-1.8)      & ?? (-1.9)      & -1.8 (-2.1)    &    -0.46 (-0.84; Tim)         \\ 
    \\
    Net CRE      & 0.3 (0.3)  & ?? (0.0)  & -0.1(-0.1)    & ?? (-0.0)         & 0.1 (0.1)          & 0.65   \\  
    \\
    LW CRE       & 0.4 (0.4)  & ?? (0.2)  & 0.1 (0.2)  & ?? (0.2)        & 0.1 (0.1)          & 0.14    \\  
    \\
    SW CRE      & -0.7 (-0.7) & ?? (-0.2) & -0.1 (-0.1)  & ?? (-0.1)      & -0.2 (-0.2)         & -0.5              \\  
    \\
    LW CLR       & 2.0 (2.0)  & ?? (2.3) & 2.0 (2.3)   & ??  (2.3)       & 2.0 (2.4)         & 1.7             \\  
    \\
    SW CLR      & -0.1 (-0.1)  & ?? (-0.4) & -0.3 (-0.4)    & ?? (-0.4)        & -0.3 (-0.4)          & -0.6                   \\  \hline

@@

>>>>

\documentclass[11pt]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{epstopdf}

@@

\begin{abstract}
Clouds observed from multiple satellites are compared to the clouds simulated by GFDL's new AM4 climate model.  
The new atmospheric climate model succeeded at significantly reducing the TOA radiative flux biases as compared 
to CERES observations.  Despite a relatively low top-of-atmosphere sensitivity to uniform warming of SSTs 
(Cess-type warming experiments), the corresponding coupled climate model, CM4, has high transient and 
equilibrium climate sensitivities.

@@

\textbf{Key Points}
\begin{itemize}
  \item{The AM4.0 TOA cloud radiative effect shows small biases compared with CERES-EBAF observations, both versions 
  2.8 and 4.1.}
  \item{Too few clouds are simulated by AM4.0 at high, middle, and low-levels, as compared to observations from CALIPSO.}
  \item{AM4.0 low-level clouds have a negative bias (relative to MISR) that is larger for thin clouds, relative to thick.}
  \item{Various configurations of a single global climate model lead to climate sensitivities that range from 2.1K (Cess) to 
  about 5K (Winton's ECS).}
\end{itemize}

@@

% thoughts from Zhao et al. 2018 part 1, section 4
% Attention to the observed TOA radiative fluxes were given a high priority during the development of AM4.0 first 
% of the relatively high confidence in the observations, and second because it was anticipated that these fluxes
% are an important component in the coupled simulations of CM4.0.   Figure 2 shows that AM4.0 does a better 
% job simulating RLUT and RSUT than any other of the compared CMIP5 models.   Not only was the global 
% mean bias of (-0.77 W/m2) an improvement over AM3 and AM2.1 (-4.11 and -3.16 W/m2), but the spatial pattern 
% was improved over almost the entire world ocean.   Fluxes at the TOA for AM4.0 largely corrected over reflection
% throughout most of the oceans and an over absorption of solar radiation in the Southern Hemisphere ocean 
% south of ~60 degrees.

From Poster
It has been known for decades that  the spread of cloud feedbacks among models contributes to a large portion of the spread in climate sensitivity among those same models (Cess et al., 1989; Bony and Dufresne, 2005).  It also now clear that the climate sensitivity estimated from constant temperature perturbation experiments is not a good indicator of the climate sensitivity that is estimated from regression techniques of abrupt 4xCO2 warming experiments (e.g. Andrews et al., 2012), and that both of these measures of sensitivity underestimate the equilibrium sensitivity that is attained when a coupled climate model reaches equilibrium after multiple millennia (Paynter et al., 2018).

Variation of the climate sensitivity within individual models has been tied to the influence of particular surface temperature patterns.  This work assesses the fidelity of the clouds in AM4.0/CM4.0 with observations and compares clouds from experiments with differing sensitivities. 
end from Poster

@@

\begin{figure}
% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 1
  \includegraphics[width=0.95\columnwidth]{/Users/silvers/Research/cfmip_paper/cf_misr_cldfrac_allheights.eps}
  \caption{Observed and modeled clouds for all heights.  Clouds shown are divided into thick (optical depth between 3.6 and 23) 
  and thin (optical depth between 0.3 and 3.6) 
  clouds.  The observations (bottom) are from the MISR satellite (2000-2013) and the modeled clouds (top) were 
  derived with the MISR simulator.  Mean cloud fraction values for MISR 
  (AM4) are 32\% (24\%) for thick clouds and 22\% (12\%) for thin clouds.}
  \label{fig:misr}
\end{figure}

\begin{figure}
% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 3
  \includegraphics[width=0.86\columnwidth]{/Users/silvers/Research/cfmip_paper/cf_misr_cldfrac_below3km.eps}
  \caption{As in previous figure except that here only clouds below 3km are shown.  Clouds shown are divided into thick 
  (optical depth between 3.6 and 23) and thin (optical depth between 0.3 and 3.6) 
  clouds.  The observations (bottom) are from the MISR satellite (2000-2013) and the modeled clouds (top) were derived 
  with the MISR simulator (amip experiment). Mean cloud fraction values for MISR 
  (AM4) are 21\% (17\%) for thick clouds and 17\% (6\%) for thin clouds}
  \label{fig:calipso_sim_vs_mod}
\end{figure}

@@

\begin{figure}
% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 1
  \includegraphics[width=0.75\columnwidth]{cfmipfigs/ISCCP_CALIPSO_clt_correctedBiasPattern_nogrid.eps}
  %\includegraphics[width=0.75\columnwidth]{cfmipfigs/clt_isccp_calipso_am4_4pan.eps}
  \caption{Comparison of total cloud fraction from AM4 with two observational data sets: ISCCP (left) and CALIPSO (right).}
  \label{fig:clt_isccp_calipso}
\end{figure}

@@

The recent model development efforts at GFDL, and participation in CMIP6/CFMIP have provided a 
unique/valuable opportunity to analyze a group of models that are built on the same code base while 
spanning a wide range of model configurations.  The model types include (should we include any of the
efforts from the RCE or Walker Cell configurations?) an Aquaplanet, an AGCM (AM4.0), 
and an AOGCM (CM4.0).  When combined with a variety of boundary conditions this creates a hierarchy of
models which are all derived from or dependent on the same atmospheric code base (AM4.0).  
%It is a bit like a group of siblings sharing the same gene pool but at various stages of intelligence or education.      
Our hypothesis for this study is that the large range of climate sensitivities that are found within this 
group of models is in large part due to variations in the clouds (both their climatology and their feedbacks).
The clouds in these simulations respond to a variety of different conditions including different
patterns of prescribed SST, the presence or absence of land/ice, and in the case of the aquaplanet
experiments, a lack of cloud-aerosol interactions which are present in the amip and coupled experiments.

Due to a combination of changing computing power and differing priorities, the sensitivity of Earth's climate to 
perturbations has been estimated in many different ways.  Three very common methods are documented 
here.  First, the climate sensitivity can be estimated from the change in radiative flux at the top of the 
atmosphere after imposing a prescribed change of surface temperature.  This method of using SST changes
as a proxy for climate change was pioneered by Robert Cess (e.g. 1989, 1990).  Second, the climate
sensitivity can be estimated from a fully coupled experiment in which the CO2 concentration is instantaneously 
quadrupled relative to the pre-Industrial values.  Linear regression can then be used to estimate the 
sensitivity of the model (Gregory et al., 2004, Andrews we al., 2012, IPCC).  This is the origin of the 
so-called equilibrium climate sensitivity in Andrews et al., 2012 and the IPCC.  Third, the climate sensitivity
can be computed from simply measuring the change of surface temperature after the CO2 concentration
has been doubled in a fully coupled climate model following an increase of 1\% per year in the CO2 concentration.
This defines the transient climate response.

The DECK experiments of CMIP6 can be used to provide a measure of the climate sensitivity based on 
three different fully coupled experiments.  The methods used to determine the sensitivity are distinct, and the resulting 
differences in the measures of sensitivity reveal important details of the physics that underly the response
of the climate system to a perturbation such as increasing concentrations of carbon dioxide.  The three 
experiments are the historical simulation (historical: 1850-2014),  the abrupt quadroupling of 
$\rm{CO}_2$ concentration ($abrupt-4xCO2$: 300 years), and the experiment in which the 
concentration of $\rm{CO}_2$ is increased by 1\% 
 per year from the pre-industrial value of 284.262 ppm(?units?) until the concentration is doubled ($1pctCO2$: 150 years, doubling at year 70).  
The historical simulation is our best attempt at using our coupled GCM to reproduce the historical 
record found in observations.  This has frequently been used to estimate the climate sensitivity using the 
energy budget method (Otto et al., 2013, Armour et al., Andrews et al., Winton et al., 2020).  The 
$abrupt-4xCO2$
experiment has been utilized by the IPCC to derive measures ECS among the CMIP5 and CMIP6 models
using a linear regression of the change in TOA radiative fluxes and surface air temperature over the first 
150 years of simulation (Gregory et al., 2004; Andrews et al., 2012).  In contrast to the abrupt change of 
$\rm{CO}_2$ concentration, the $1pctCO2$ experiment allows the Earth system to adjust to 
a 1 \% per year increasing of $\rm{CO}_2$ concentration until they are doubled relative to the 
pre-Industrial values.  The sensitivity at this point is defined 
as the Transient Climate Response (TCR).  The TCR is the relevant measure of climate sensitivity for 
near term climate change because it is expected that the atmospheric concentrations of $\rm{CO}_2$ 
will reach (insert 2xCO2 value) around the middle of this century.

@@

Plotting the cloud fields as a function of latitude and height highlights some of the similarities and differences 
between the various experiments.  In general the clouds in the $amip$ and historical simulations are similar to 
each other, as we would expect.  The differences between the clouds of these experiments are due to the 
different SST pattern that the two experiments have.  We can thus see how the clouds change as a result 
of SST biases over the observational period.  Two warming experiments have been plotted, amip p4K and 
the coupled abrupt 4xCO2 experiment.  The cloud fields in these experiments are similar to each other, with 
the differences again likely coming from the different SST patterns that result from a fully coupled system.  The 
cooling experiment is rather unique and tends to have cloud fraction changes in the opposite direction as 
the warming experiments.

%% Beta feedback??  relavent?
%Brient and Bony (2012) proposed what they call the $\beta$ feedback as a way to quantify whether or not ' models have 
%changes in low-cloud cloud radiative effects which are proportional to the strength of the cloud radiative effects of their
%low clouds.'  See $\it{Stevens etal, Cookie Overview}$ for details.   That paper asks the question of whether single 
%model relationships between low-cloud amounts and the sensitivity of low clouds to warming can be 
%masked by changes in multi-model ensembles.  This should be checked for the GFDL model in this paper.  
%
%The cloud radiative effect (CRE) is computed as the difference between the all-sky and clear-sky TOA fluxes.

\begin{table}
\begin{center}
\caption{Global mean radiative feedbacks ($\rm{W\, m^{-1} K^{-1}}$).  The cloud radiative effect (CRE) is computed as
 the clear sky minus all sky flux. The values for the Abrupt 4xCO2 experiment
have been estimated from a linear fit of the years 51-300.  Compare to Ringer et al. 2014.
Values in parenthesis are most recent values.  Why are they different than the Amip p4K 
original values?}
    \begin{tabular}{*{7}{c}}
    \hline
    \hline
 Feedback & Aqua p4K & Amip m4K & Amip p4K &  Amip p8K & Amip Future & Abrupt 4xCO2    \\ \hline
    Net          &   -2.2 (-2.2) & ?? (-1.9)  &  -1.6 (-1.8)      & ?? (-1.9)      & -1.8 (-2.1)    &    -0.46 (-0.84; Tim)         \\ 
    \\
    Net CRE      & 0.3 (0.3)  & ?? (0.0)  & -0.1(-0.1)    & ?? (-0.0)         & 0.1 (0.1)          & 0.65   \\  
    \\
    LW CRE       & 0.4 (0.4)  & ?? (0.2)  & 0.1 (0.2)  & ?? (0.2)        & 0.1 (0.1)          & 0.14    \\  
    \\
    SW CRE      & -0.7 (-0.7) & ?? (-0.2) & -0.1 (-0.1)  & ?? (-0.1)      & -0.2 (-0.2)         & -0.5              \\  
    \\
    LW CLR       & 2.0 (2.0)  & ?? (2.3) & 2.0 (2.3)   & ??  (2.3)       & 2.0 (2.4)         & 1.7             \\  
    \\
    SW CLR      & -0.1 (-0.1)  & ?? (-0.4) & -0.3 (-0.4)    & ?? (-0.4)        & -0.3 (-0.4)          & -0.6                   \\  \hline

@@

The previous section showed that the AM4.0 amip simulations underestimates clouds relative to the CALIPSO observations.  
Simulations over the historical period with the fully coupled model do not improve on this bias, and in the case of the abrupt
4xCO2 and gradual 1\% CO2 experiments the bias is worse at almost all latitudes except at 20 degrees south.  The two coupled
warming experiments (abrupt and ramp) have some interesting differences from both the \textit{amip} and the
 \textit{historical} simulations.   These warming experiments have a distinct peak (about 5\%) of low-level cloud fraction at about 20N that 
 both \textit{amip} and \textit{historical} lack (\textit{historical} does have a small but less distinct peak).  Additionally, 
 while the low-level clouds of the \textit{amip} and \textit{historical} experiments are almost identical between 10-60N, the 
 \textit{abrupt} and \textit{ramp} experiments show a large decrease of cloud fraction between about 30-70N.  Is this decrease
 of low-level cloud in the NH responsible for a stronger sw cloud feedback relative to the amip p4K and historical simulations?  Of the 
 two experiments, the abrupt has the least amount of low-level cloud.  Does it also then have the strongest/largest SW CRE?  
 When comparing these experiments to the CERES0-EBAF observations from the observational period the \textit{abrupt} and 
 \textit{ramp} experiments match the CERES-EBAF CRE better than the amip or historical experiments.  All of the AM4.0 
 simulations shown here compare best with the CERES-EBAF v2.8.  This is likely because this is the version of the data that 
 was used as a reference during the model development.  For comparison we also show the CERES-EBAF v4.1 data.  Although 
 differences between the two versions are clear, the AM4.0 models compare relatively well to both.  The differences between 
 the two observational version are mostly contained to the latitudes between +/- 30.  This excellent agreement with observations 
 of the CRE in the NH for the warming experiments was surprising, but does not in general indicate better observational 
 agreement of the warming experiments relative to the \textit{historical} and \textit{amip} experiments.   These warming 
 experiments have a very strong arctic and southern ocean response that differs significantly from the historical observations 
 and simulations.   As these are signature CRE changes in a warming climate it is not surprising that they are not 
 present in the historical data.

\begin{figure}
  \includegraphics[width=0.86\columnwidth]{cfmipfigs/meridional_CRE_CERES2p8.eps}
  \caption{.}
  \label{fig:CRE_multiexperiments_ceres}
\end{figure}
